An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-06-26 EconGrowth.Rnw
prepping for residual resampling

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************
  eval=TRUE,
  # ********************************************************
  # Allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  dev='tikz',    
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
source("Econ-Growth-Functions2.R")
@

>>>>

<<setup, echo=FALSE, message=FALSE, eval=FALSE>>=
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************
  eval=TRUE,
  # ********************************************************
  # Allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  dev='tikz',    
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
source("Econ-Growth-Functions2.R")
@
